---
title: "Stack Exchange Classification2"
output: html_notebook
---

load required packages

```{r}

library(dplyr)
library(tidytext)
library(ggplot2)
library(RTextTools)
library(caret)

```

load input files

```{r}
getwd()
#fileloc="/Users/aankurbhatia/Documents/Datasets/stack exchange/Stack-exchange-classification/"
biology=read.csv(file = "biology.csv",stringsAsFactors = FALSE)
cooking=read.csv(file = "cooking.csv",stringsAsFactors = FALSE)
crypto=read.csv(file = "crypto.csv",stringsAsFactors = FALSE)
diy=read.csv(file = "diy.csv",stringsAsFactors = FALSE)
robotics=read.csv(file ="robotics.csv",stringsAsFactors = FALSE)
travel=read.csv(file = "travel.csv",stringsAsFactors = FALSE)
```

remove id varibles from all datasets and rbind all datasets into one training dataset

```{r}

biology$id=NULL
cooking$id=NULL
crypto$id=NULL
diy$id=NULL
robotics$id=NULL
travel$id=NULL

train=rbind(biology,cooking,crypto,diy,robotics,travel)
test=read.csv(file = "test.csv",stringsAsFactors = FALSE)
submission=read.csv(file ="sample_submission.csv",stringsAsFactors = FALSE)
rm(biology,cooking,crypto,diy,robotics,travel)
```

Let's remove the content from both train and test datasets. also, we remove the ID from test dataset and store it as a separate variable. 

Also we create a vector source (corpus) of the title for train set

```{r}
train_content=train$content
train$content=NULL
testID=test$id
test_content=test$content
test$id=NULL
test$content=NULL

library(tm)
source1=VectorSource(train$title[1:30000])
source2=VectorSource(train$title[30001:60000])
source3=VectorSource(train$title[60001:87000])
corpus1=Corpus(source1)
corpus2=Corpus(source2)
corpus3=Corpus(source3)
```

clean the corpus using the tm_map commands

```{r}
corpus1=tm_map(corpus1,content_transformer(tolower))
corpus2=tm_map(corpus2,content_transformer(tolower))
corpus3=tm_map(corpus3,content_transformer(tolower))
#corpus=tm_map(corpus,removeNumbers) # we do not remove numbers
corpus1=tm_map(corpus1,removePunctuation)
corpus2=tm_map(corpus2,removePunctuation)
corpus3=tm_map(corpus3,removePunctuation)
corpus1=tm_map(corpus1,stripWhitespace)
corpus2=tm_map(corpus2,stripWhitespace)
corpus3=tm_map(corpus3,stripWhitespace)
corpus1=tm_map(corpus1,removeWords,stopwords('english'))
corpus2=tm_map(corpus2,removeWords,stopwords('english'))
corpus3=tm_map(corpus3,removeWords,stopwords('english'))


```

convert to DocumentTerm Matrix- then convert to term matrix , inverse term frequency

```{r}
mat1=DocumentTermMatrix(corpus1)
mat2=DocumentTermMatrix(corpus2)
mat3=DocumentTermMatrix(corpus3)
inspect(mat1[1:2,1000:1005])
matwt1=weightTfIdf(mat1)
matwt2=weightTfIdf(mat2)
matwt3=weightTfIdf(mat3)
inspect(matwt1[1:4,1500:1510])
matmat1=as.matrix(matwt1)
matmat2=as.matrix(matwt2)
matmat3=as.matrix(matwt3)
```

Build 3 separate models using matmat, later combine the matrices to build one models

```{r}
container1=create_container(matmat1,train$tags[1:30000],trainSize = 1:15000,testSize = 15001:30000,virgin = FALSE)
model=train_model(container1,'SVM',kernel = 'linear')
```


